---
title: "Stat159 Fall2016 Project2"
author: "Jamie Stankiewiz, Philhoon Oh"
date: "October 30, 2016"
output: pdf_document
---
```{r setup5, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
scaled_credit = read.csv("../data/scaled-credit.csv")
library(xtable)
load("../data/ols-regression.RData")
load("../data/ridge-regression.RData")
load("../data/lasso-regression.RData")
load("../data/pcr-regression.RData")
load("../data/plsr-regression.RData")
```

```{r child = 'sections/00-abstract.Rmd'}
```

```{r child = 'sections/01-introduction.Rmd'}
```

```{r child = 'sections/02-data.Rmd'}
```

```{r child = 'sections/03-methods.Rmd'}
```

```{r child = 'sections/04-analysis.Rmd'}
```

```{r child = 'sections/05-results.Rmd'}
```

```{r child = 'sections/06-conclusion.Rmd'}
```


#Tables and Figures

```{r echo = FALSE, results='asis'}
  scaled_credit2 = scaled_credit[,-1]
  scaled_credit3 = scaled_credit2[,1:5]
  x = xtable(head(scaled_credit3), digits=4)
  print(x, comment=FALSE, type='latex', include.rownames = FALSE)
  scaled_credit4 = scaled_credit2[,6:length(scaled_credit2)]
  x = xtable(head(scaled_credit4), digits=4, ,caption = "First 6 results of Premodeling data processing results")
  print(x, comment=FALSE, type='latex', include.rownames = FALSE)
  
  
```


```{r echo = FALSE, results='asis'}
load( "../data/anova-qual.RData")

x = xtable(anova_ethnicity, digits=2, caption = "Anova analysis of ethnicity and Balance")

print(x, comment=FALSE, type="latex")

x = xtable(anova_gender, digits=2, caption = "Anova analysis of gender and Balance")
print(x, comment=FALSE, type="latex")

x = xtable(anova_marriage, digits=2, caption = "Anova analysis of marriage and Balance")
print(x, comment=FALSE, type="latex")

x = xtable(anova_student, digits=2, caption = "Anova analysis of student and Balance")
print(x, comment=FALSE, type="latex")

```


```{r echo = FALSE, results='asis'}
x = xtable(reg2, digits=4, caption = "MODEL1 using selected predictor variables: income, limit, rating, cards, ages, eduction, student")
print(x, comment=FALSE, type='latex')

```
  
```{r echo = FALSE, results='asis'}
x = xtable(reg3, digits=4, caption = "MODEL2 using Optimal predictor variables: income, limitm cards, student")
print(x, comment=FALSE, type='latex')

```

```{r echo = FALSE, results='asis'}
  k = data.frame(Adjusted.R.Square= c("Model1","Model2"),
                 Value = c(summary(reg2)$adj.r.squared,summary(reg3)$adj.r.squared))
  x=xtable(k,digits=4, caption = "Adjusted R Square of Model1 and Model2")
  print(x, comment=FALSE, type = 'latex')

```
  
  
```{r echo = FALSE, results='asis'}
  ols_cof = as.data.frame(t(as.data.frame(cof_ols)))
  ridge_cof = as.data.frame(t(as.data.frame(cof_ridge)))
  lasso_cof = as.data.frame(t(as.data.frame(cof_lasso)))
  pcr_cof = as.data.frame(cof_pcr)
  plsr_cof = as.data.frame(cof_plsr)
  
  off_cof = as.data.frame(t(rbind(ols_cof,ridge_cof,lasso_cof,pcr_cof,plsr_cof)))
  names(off_cof) = c("OLS", "RR", "LASSO", "PCR", "PLSR")
  
  off_cof_xt = xtable(off_cof, digits =4, caption = "Official Coefficients of all Regression Methods")
  print(off_cof_xt, comment=FALSE, type = 'latex')
  
   
```


```{r echo=FALSE, results='asis'}
  names <- c('OLS', 'Ridge', 'Lasso', 'PCR', 'PLSR')
  mse_values <- c(test_mse_ols, test_mse_ridge, test_mse_lasso, test_mse_pcr, test_mse_plsr)
  results = data.frame(RegressionMethods = names, MSE = mse_values)
  x=xtable(results, digits = 4, caption = "Test MSE of all regression methods")
  print(x, comment=FALSE, type='latex', include.rownames=FALSE)

```


```{r echo=FALSE, results='asis'}
  cof_best = as.data.frame(cof_plsr)
  cof_best1 = cof_best[1:5]
  cof_best2 = cof_best[6:12]
  x1=xtable(cof_best1, digits = 4)
  x2=xtable(cof_best2, digits = 4, caption = "The official coefficients of best model(PLSR Regression)")
  print(x1, comment=FALSE, type='latex')
  print(x2, comment=FALSE, type='latex')

```




\begin{figure}[b]
  \begin{center}
    \caption{Residuals plot of OLS on the test dataset}
    \centering
      \includegraphics[width=4in]{../../images/ols-residuals.png}
  \end{center}
\end{figure}
  
  
\begin{figure}[!b]
  \begin{center}
    \caption{Plot of the cross-validtion errors of Ridge Regression on Lambda}
    \centering
      \includegraphics[width=4in]{../../images/ridge-cross-validation-errors.png}
  \end{center}
\end{figure}


\begin{figure}[!b]
  \begin{center}
    \caption{Plot of the cross-validtion errors of Lasso Regression on Lambda}
    \centering
      \includegraphics[width=4in]{../../images/lasso-cross-validation-errors.png}
  \end{center}
\end{figure}


\begin{figure}[!b]
  \begin{center}
    \caption{Plot of the cross-validtion errors of PCR Regression on M}
    \centering
      \includegraphics[width=4in]{../../images/pcr-cross-validation-errors.png}
  \end{center}
\end{figure}


\begin{figure}[!b]
  \begin{center}
    \caption{Plot of the cross-validtion errors of PLSR Regression on M}
    \centering
      \includegraphics[width=4in]{../../images/plsr-cross-validation-errors.png}
  \end{center}
\end{figure}