---
title: "Predictive Modeling Report"
author: "Jamie Stankiewiz  and Philhoon Oh"
date: "November 4, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## References

The information, code and methods in this report is based off of the book: "An Introduction to Statistical Learning"" by James et al.

Chapter 6: _Linear Model Selection to Statistical Learning_

We will be using the data set: Credit.csv

## Goals

Alternative Model Fitting using:

- OLS (Orindary Least Squares)
- RR (Ridge Regression)
- LR (Lasso Regression)
- PCR (Principle Components Regression)
- PLSR (Partial Least Squares Regression)

We will be using these 5 methods to generate the response variable.  We will then determine which regression model produces the best response variable.

## Variables

  Predictor Variables: 
  
    Income, Limit, Rating, Cards, Age, Education, Gender, Student, Married, Ethnicity
  
  Response Variable:
  
    Balance

## A look at the Credit data set

```{r}

credit=read.csv("../data/Credit.csv")  
head(credit)[,-1]
```


## Pre-processing the data set

In order to use the data set, we must convert qualitative variables into 0/1 slots.  This makes it better for statisticans to work with.

Here's a look:

```{r}

new_credit = read.csv('../data/new-credit.csv')
new_credit[1:3,-1]
```

##

Now in order to use the data set for our regression models, we must standardize the data.

Here's a look at the new data set: scaled_credit.csv

```{r}

scaled_credit = read.csv("../data/scaled-credit.csv")  
scaled_credit[1:3,-1]
```



## 
