---
title: "Predictive Modeling Report"
author: "Jamie Stankiewiz  and Philhoon Oh"
date: "November 4, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## References

The information, code and methods in this report is based off of the book: "An Introduction to Statistical Learning"" by James et al.

Chapter 6: _Linear Model Selection to Statistical Learning_

We will be using the data set: Credit.csv

## Goals

Alternative Model Fitting using:

- OLS (Orindary Least Squares)
- RR (Ridge Regression)
- LR (Lasso Regression)
- PCR (Principle Components Regression)
- PLSR (Partial Least Squares Regression)

We will be using these 5 methods to generate the response variable.  We will then determine which regression model produces the best response variable.

## Variables

  Predictor Variables: 
  
    Income, Limit, Rating, Cards, Age, Education, Gender, Student, Married, Ethnicity
  
  Response Variable:
  
    Balance

## A look at the Credit data set

```{r}

credit=read.csv("../data/Credit.csv")  
head(credit)[,-1]
```


## Pre-processing the data set

In order to use the data set, we must convert qualitative variables into 0/1 slots.  This makes it better for statisticans to work with.

Here's a look:

```{r}

new_credit = read.csv('../data/new-credit.csv')
new_credit[1:3,-1]
```

##

Now in order to use the data set for our regression models, we must standardize the data.

Here's a look at the new data set: scaled_credit.csv

```{r}

scaled_credit = read.csv("../data/scaled-credit.csv")  
scaled_credit[1:3,-1]
```


## Overview of the Regressions

- Oridnary Least Squares

_Shrinkage Methods_

\smallfont _shrinking the coefficients and the variance_

- Ridge Regression
- Lasso Regression

_Dimension Reduction Methods_

\smallfont _getting rid of variables that aren't significant_

- Principle Components Regression
- Partial Least Squares Regression


##Ordinary Least Squares

**Goal**: To minimize the sum of the squares between the observed and predicted values.

```{r, echo=FALSE}

load('../data/ols-regression.Rdata')
load('../data/scale-train-test.RData')
```
We need to figure out which variables have a significant effect on the response variable.  To do so, we look at the regression summary of all the predictors on the response (balance).


> we can see that only income, limit, cards, and student are the only predictors that have a significant effect on balance.

##{.smaller}
```{r, echo=TRUE}
reg = lm(balance ~ income+limit+rating+cards+age+education+student+gender+marriage+asian+caucasian
         , data = scaled_credit_train)
sum_reg = summary(reg)
sum_reg
```

## OLS MSE

By only using income, limit, cards and student to predict response, we can find the MSE on the full data set.

test MSE:

```{r, echo=TRUE}
test_mse_ols
```

full MSE (full data set):
```{r, echo=TRUE}
full_mse_ols
```


## Ridge Regression {.smaller}
_a shrinkage method_

Using 10-fold cross validation on a test data set (of 100) to generate an optimal lambda value.
```{r, echo=FALSE}
load('../data/ridge-regression.Rdata')
```
Optimal lambda value: 
```{r}
par_ridge
```

We then use that lambda value to determine the MSE for the test subset and the full data set:
```{r, echo=TRUE}
test_mse_ridge
full_mse_ridge
```

## Lasso Regression {.smaller}
_a shrinkage method_

Using 10-fold cross validation on a test data set (of 100) to generate an optimal lambda value.
```{r, echo=FALSE}
load('../data/lasso-regression.Rdata')
```
Optimal lambda value: 
```{r}
par_lasso
```

We then use that lambda value to determine the MSE for the test subset and the full data set:
```{r, echo=TRUE}
test_mse_lasso
full_mse_lasso
```


## PCR {.smaller}
_a dimension reduction method_

Uses 10 fold cross validation to determine how many components (predictors) have a signifciant effect on the response variable. 
```{r, echo=FALSE, include=F}
load('../data/pcr-regression.Rdata')
library(pls)
set.seed(0)
pcr.fit <- pcr(balance~., data = scaled_credit_train, validation='CV', scale = FALSE)
M = which(pcr.fit$validation$PRESS==min(pcr.fit$validation$PRESS))
```
in this case, the number of components that are significant to the regression (out of 11) is:
```{r}
M
```

```{r, echo=TRUE}
test_mse_pcr
full_mse_pcr

```

## PLSR {.smaller}
_a dimension reduction method_

Uses 10 fold cross validation to determine how many components (predictors) have a signifciant effect on the response variable. 
```{r, echo=F, include=F}
load('../data/plsr-regression.Rdata')
set.seed(0)
pls.fit = plsr(balance~., data = scaled_credit_train, validation='CV', scale = FALSE)
M = which(pls.fit$validation$PRESS==min(pls.fit$validation$PRESS))
```
in this case, the number of components that are significant to the regression (out of 11) is:
```{r}
M
```
```{r, echo=TRUE}
test_mse_plsr
full_mse_plsr
```

