---
title: "Predictive Modeling Report"
author: "Jamie Stankiewiz  and Philhoon Oh"
date: "November 4, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## References

The information, code and methods in this report is based off of the book: "An Introduction to Statistical Learning"" by James et al.

Chapter 6: _Linear Model Selection to Statistical Learning_

We will be using the data set: Credit.csv

## Goals

Alternative Model Fitting using:

- OLS
- Ridge Regression
- Lasso Regression
- PCR
- PLSR

We will be using these 5 methods to generate the response variable.  We will then determine which regression model produces the best response variable.

## Variables

  Predictor Variables: 
  
    Income, Limit, Rating, Cards, Age, Education, Gender, Student, Married, Ethnicity
  
  Response Variable:
  
    Balance

## A look at the Credit data set

```{r}

credit=read.csv("../data/Credit.csv")  
head(credit)[,-1]
```



## Slide with Plot

```{r pressure}
plot(pressure)
```

